A decomposition Approach for solving the JSP using multi-shot ASP\thanks{Supported by organization x.}

### 2022-02-03 ICLP Paper/samplepaper.tex
taking out red text color
set page numbers to 14
changed placement of decomposition encoding to bottom of page
update 2nd Table
added own related work in conclusions

\newcommand{\clingo}{\emph{clingo}\xspace}
\newcommand{\clingodl}{\emph{clingo}[DL]\xspace}
\newcommand{\figspace}{\vspace{-1ex}}
\newcommand{\ksverify}[1]{\textcolor{red}{#1}}
\makeatletter
\def\fcapsize@figure{\normalfont\normalsize\rmfamily}
\def\fcapstyle@figure{\normalfont\normalsize\itshape}
\makeatother

@@

\jnlPage{1}{8}
\jnlDoiYr{2021}
\doival{10.1017/xxxxx}
%
\title{Problem Decomposition and Multi-shot ASP Solving for Job-shop Scheduling%
% \thanks{This work was partially funded by
% KWF project 28472,
% cms electronics GmbH,
% FunderMax GmbH,
% Hirsch Armbänder GmbH,
% incubed IT GmbH,
% Infineon Technologies Austria AG,
% Isovolta AG,
% Kostwein Holding GmbH, and
% Privatstiftung Kärntner Sparkasse.}%
}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
% \author{Mohammed M. S. El-Kholany\inst{1}\orcidID{0000-0002-1088-2081} \and
% Martin Gebser\inst{1,2}\orcidID{0000-0002-8010-4752} \and
% Konstantin Schekotihin\inst{1}\orcidID{0000-0002-0286-0958}}
% %
% \authorrunning{M. El-Kholany et al.}
% % First names are abbreviated in the running head.
% % If there are more than two authors, 'et al.' is used.
% %
% \institute{Alpen-Adria-Universität Klagenfurt, Klagenfurt, Austria 
% \email{\{mohammed.el-kholany, martin.gebser and konstantin.schekotihin\}@aau.at}\\
% %\url{http://www.springer.com/gp/computer-science/lncs} \and
% Technische Universität Graz, Graz, Austria\\
% \email{mgebser@ist.tugraz.at}}
\begin{authgrp}
\author{\sn{Mohammed M.\ S.} \gn{El-Kholany}} % \inst{1}\orcidID{0000-0002-1088-2081} \and
\affiliation{University of Klagenfurt, Austria \and Cairo University, Egypt}
\author{\sn{Martin} \gn{Gebser}} % \inst{1,2}\orcidID{0000-0002-8010-4752} \and
\affiliation{University of Klagenfurt, Austria \and Graz University of Technology, Austria}
\author{\sn{Konstantin} \gn{Schekotihin}} % \inst{1}\orcidID{0000-0002-0286-0958}
\affiliation{University of Klagenfurt, Austria}
\end{authgrp}

@@

\lstinputlisting[float=t,label=prg:decomposition,caption={J-EST decomposition encoding}]{listing/decomposition.lp}
% Only 
Our encoding for \emph{Job-based Earliest Starting Time (J-EST)} decomposition
in Listing~\ref{prg:decomposition} takes a JSP instance specified by facts over
\lstinline{operation/4} as input.
In addition, a constant~\lstinline{n},
set to the default value~\lstinline{2} in line~\ref{prg:predeco:tw:begin},
determines the number of time windows into which the given operations
shall be split.
As we aim at time windows of (roughly) similar size,
the target number of operations per time window is in line~\ref{prg:predeco:optw:begin}
calculated by $\lceil \text{\lstinline{N}} / \text{\lstinline{n}}\rceil$,
where \lstinline{N} is the total number of operations.
For example, we obtain \lstinline{width(5)} for partitioning the nine operations
of the JSP instance in Listing~\ref{prg:facts} into two time windows.

@@

    30\%             & $3051.2$  & $1000.0$   & $3.0$	& $3451.8$      & $1000.0$ & $4.0$ & $6933.3$ & $1000.0$ & $6.0$ % \\ 
%                     [1.5mm]
%                     
%    \\[-2.75mm]
%    
%    \multicolumn{10}{c}{\textbf{Compressing Time Windows}}\\
%    \hline
%    \multirow{2}*{Overlap} & \multicolumn{3}{c}{50$\times$15} & \multicolumn{3}{c}{50$\times$20} & \multicolumn{3}{c}{100$\times$20}\\
%     & Makespan & CPU(Sec) & IC & Makespan & CPU(Sec) & IC & Makespan & CPU(Sec) & IC \\
%     \hline\\[-2.75mm]
    \midline
    0\%              & $3013.3$  & $572.3$   & $3.7$	   & $3186.8$      & $540.8$ & $3.3$ & $5713.0$ & $589.2$ & $8.6$\\
    % [1.5mm]

    10\%             & $2970.2$  & $600.0$   & $4.0$	   & $3149.8$      & $600.0$ & $4.0$ & $5656.0$ & $600.0$ & $9.0$\\

    20\%             & $2952.2$  & $600.0$   & $4.0$	   & \boldmath{$3147.7$}      & $600.0$ & $4.0$ & \boldmath{$5619.2$} & $600.0$ & $9.0$\\

    30\%             & \boldmath{$2943.1$}  & $600.0$   & $4.0$	   & $3162.2$      & $600.0$ & $4.0$ & $5857.0$ & $600.0$ & $9.0$%\\ 
                     % [1.5mm]
    \botline %\hline
    \end{tabular}
   % }
%    \end{minipage}
% }
%    \hfill\hfill\mbox{~}
\end{table}
%
Focusing again on the static M-EST decomposition strategy,
Table~\ref{tab:Table03} assesses different percentages of overlapping
operations from previous time windows as well as the impact of compressing
(optimized) partial schedules in a postprocessing phase.
The baseline approach as above is included in the first row with 0\% of the
operations per time window overlap and without the use of compression.
The next three rows exclude compression as well but introduce 10\%, 20\%, or
30\% of overlapping operations that can be rescheduled together with operations
of the next time window.
In view of the considered number of time windows, picked according to the shortest
average makespan achieved with 0\% overlap, between $18$ and $35$ operations constitute
an overlap of 10\%, so that 30\% range up to more than $100$ operations.
Such non-negligible amounts can make the optimization of subproblems for time windows
harder, while the moderate overlaps of 10\% or 20\% manage to consistently
improve the solution quality.
Even more significant advantages are obtained by applying compression in the last
four rows,
where the average makespan gets already shorter with 0\% overlap.
Further improvements of roughly 2\% in solution quality are achieved with 20\% overlap,
which yield consistently better schedules than the smaller overlap of 10\% and
avoid deteriorations as observed with 30\% overlap on the largest instances
with $100\times20$ jobs and machines.
In summary, a Machine-based problem 
decomposition strategy along with
postprocessing to compress partial schedules as well as a modest overlap of about
20\% of the time window size turn out to be most successful for the JSP
benchmark sets under consideration.

@@

\section{Conclusions}\label{sec:conclusions}
%
Our work develops multi-shot ASP modulo DL methods for JSP solving,
based on problem decomposition into balanced time windows that respect the operation
precedence within jobs and successive makespan optimization while extending
partial schedules to a global solution.
We demonstrate that splitting highly complex JSP instances into
balanced portions, for which partial schedules of good quality can be reliably
found within tight runtime limits, leads to significantly better global solutions
than obtainable with single-shot ASP modulo DL optimization in similar runtime.
Related works taking advantage of single- \citep{abjoossctowa21a}
and multi-shot solving \citep{francescutto2021solving} by
\clingodl to tackle real-world scheduling problems evaluate threshold values
on DL variables and perform optimization by means of common 
\lstinline{#minimize} statements of \clingo rather than minimizing the
value of a DL variable like \lstinline{makespan} in Listing~\ref{prg:encoding}.
Applying a similar approach can be advantageous in our future work as it may
potentially improve computational efficiency as well as solution quality further
and is even a necessity to switch from the makespan as optimization objective to tardiness
w.r.t.\ deadlines, which are crucial in many application areas.
Moreover, we aim to generalize our methods further, e.g.,
by considering flexible machine allocations and varying processing times,
and scale them up to large-scale instances with an order of magnitude more
operations than in synthetic benchmarks.
%
% In this work, different decomposition strategies have been proposed for solving the Job-shop Scheduling Problem (JSP) using a multi-shot Answer Set Programming with Difference Logic constraints to handle the decomposition approach and the problem constraints. The proposed model split the problem into sub-problems using different decomposition strategies and then optimized each separately while minimizing the Makespan. The proposed model has been developed to improve the performance by applying the overlap between TWs to fix the decomposition mistakes. In addition, the compression of each window is to fulfill the gaps that occurred during the optimization process. We tested our model on a set of benchmark instances and the experiments have shown that i) considering the bottleneck machines during the decomposition process is effective, ii) The overlap between TWs improves the solution quality, and iii) the compression of TWs is super practical, as it aided the proposed model to obtain better solutions in less computational time. Our work can be extended by linking the optimization model with a simulator that considers more realistic factors such as machine breakdowns, new job arrivals and order cancellations.

>>>>

\newcommand{\clingo}{\emph{clingo}\xspace}
\newcommand{\clingodl}{\emph{clingo}[DL]\xspace}
\newcommand{\figspace}{\vspace{-1ex}}
\newcommand{\ksverify}[1]{#1}%{\textcolor{red}{#1}}
\makeatletter
\def\fcapsize@figure{\normalfont\normalsize\rmfamily}
\def\fcapstyle@figure{\normalfont\normalsize\itshape}
\makeatother

@@

\jnlPage{1}{14}
\jnlDoiYr{2021}
\doival{10.1017/xxxxx}
%
\title{Problem Decomposition and Multi-shot ASP Solving for Job-shop Scheduling%
% \thanks{This work was partially funded by
% KWF project 28472,
% cms electronics GmbH,
% FunderMax GmbH,
% Hirsch Armbänder GmbH,
% incubed IT GmbH,
% Infineon Technologies Austria AG,
% Isovolta AG,
% Kostwein Holding GmbH, and
% Privatstiftung Kärntner Sparkasse.}%
}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
% \author{Mohammed M. S. El-Kholany\inst{1}\orcidID{0000-0002-1088-2081} \and
% Martin Gebser\inst{1,2}\orcidID{0000-0002-8010-4752} \and
% Konstantin Schekotihin\inst{1}\orcidID{0000-0002-0286-0958}}
% %
% \authorrunning{M. El-Kholany et al.}
% % First names are abbreviated in the running head.
% % If there are more than two authors, 'et al.' is used.
% %
% \institute{Alpen-Adria-Universität Klagenfurt, Klagenfurt, Austria 
% \email{\{mohammed.el-kholany, martin.gebser and konstantin.schekotihin\}@aau.at}\\
% %\url{http://www.springer.com/gp/computer-science/lncs} \and
% Technische Universität Graz, Graz, Austria\\
% \email{mgebser@ist.tugraz.at}}
\begin{authgrp}
\author{\sn{Mohammed M.\ S.} \gn{El-Kholany}} % \inst{1}\orcidID{0000-0002-1088-2081} \and
\affiliation{University of Klagenfurt, Austria \and Cairo University, Egypt}
\author{\sn{Martin} \gn{Gebser}} % \inst{1,2}\orcidID{0000-0002-8010-4752} \and
\affiliation{University of Klagenfurt, Austria \and Graz University of Technology, Austria}
\author{\sn{Konstantin} \gn{Schekotihin}} % \inst{1}\orcidID{0000-0002-0286-0958}
\affiliation{University of Klagenfurt, Austria}
\end{authgrp}

@@

\lstinputlisting[float=b,label=prg:decomposition,caption={J-EST decomposition encoding}]{listing/decomposition.lp}
% Only 
Our encoding for \emph{Job-based Earliest Starting Time (J-EST)} decomposition
in Listing~\ref{prg:decomposition} takes a JSP instance specified by facts over
\lstinline{operation/4} as input.
In addition, a constant~\lstinline{n},
set to the default value~\lstinline{2} in line~\ref{prg:predeco:tw:begin},
determines the number of time windows into which the given operations
shall be split.
As we aim at time windows of (roughly) similar size,
the target number of operations per time window is in line~\ref{prg:predeco:optw:begin}
calculated by $\lceil \text{\lstinline{N}} / \text{\lstinline{n}}\rceil$,
where \lstinline{N} is the total number of operations.
For example, we obtain \lstinline{width(5)} for partitioning the nine operations
of the JSP instance in Listing~\ref{prg:facts} into two time windows.

@@

    30\%             & $3051.2$  & $1000.0$   & $3.0$	& $3451.8$      & $1000.0$ & $4.0$ & $6933.3$ & $1000.0$ & $6.0$ % \\ 
%                     [1.5mm]
%                     
%    \\[-2.75mm]
%    
%    \multicolumn{10}{c}{\textbf{Compressing Time Windows}}\\
%    \hline
%    \multirow{2}*{Overlap} & \multicolumn{3}{c}{50$\times$15} & \multicolumn{3}{c}{50$\times$20} & \multicolumn{3}{c}{100$\times$20}\\
%     & Makespan & CPU(Sec) & IC & Makespan & CPU(Sec) & IC & Makespan & CPU(Sec) & IC \\
%     \hline\\[-2.75mm]
    \midline
    0\%              & $3013.3$  & $972.3$   & $3.7$	   & $3186.8$      & $940.8$ & $3.3$ & $5713.0$ & $989.2$ & $8.6$\\
    % [1.5mm]

    10\%             & $2970.2$  & $1000.0$   & $4.0$	   & $3149.8$      & $1000.0$ & $4.0$ & $5656.0$ & $1000.0$ & $9.0$\\

    20\%             & $2952.2$  & $1000.0$   & $4.0$	   & \boldmath{$3147.7$}      & $1000.0$ & $4.0$ & \boldmath{$5619.2$} & $1000.0$ & $9.0$\\

    30\%             & \boldmath{$2943.1$}  & $1000.0$   & $4.0$	   & $3162.2$      & $1000.0$ & $4.0$ & $5857.0$ & $1000.0$ & $9.0$%\\ 
                     % [1.5mm]
    \botline %\hline
    \end{tabular}
   % }
%    \end{minipage}
% }
%    \hfill\hfill\mbox{~}
\end{table}
%
Focusing again on the static M-EST decomposition strategy,
Table~\ref{tab:Table03} assesses different percentages of overlapping
operations from previous time windows as well as the impact of compressing
(optimized) partial schedules in a postprocessing phase.
The baseline approach as above is included in the first row with 0\% of the
operations per time window overlap and without the use of compression.
The next three rows exclude compression as well but introduce 10\%, 20\%, or
30\% of overlapping operations that can be rescheduled together with operations
of the next time window.
In view of the considered number of time windows, picked according to the shortest
average makespan achieved with 0\% overlap, between $18$ and $35$ operations constitute
an overlap of 10\%, so that 30\% range up to more than $100$ operations.
Such non-negligible amounts can make the optimization of subproblems for time windows
harder, while the moderate overlaps of 10\% or 20\% manage to consistently
improve the solution quality.
Even more significant advantages are obtained by applying compression in the last
four rows,
where the average makespan gets already shorter with 0\% overlap.
Further improvements of roughly 2\% in solution quality are achieved with 20\% overlap,
which yield consistently better schedules than the smaller overlap of 10\% and
avoid deteriorations as observed with 30\% overlap on the largest instances
with $100\times20$ jobs and machines.
In summary, a Machine-based problem 
decomposition strategy along with
postprocessing to compress partial schedules as well as a modest overlap of about
20\% of the time window size turn out to be most successful for the JSP
benchmark sets under consideration.

@@

\section{Conclusions}\label{sec:conclusions}
%
Our work develops multi-shot ASP modulo DL methods for JSP solving,
based on problem decomposition into balanced time windows that respect the operation
precedence within jobs and successive makespan optimization while extending
partial schedules to a global solution.
We demonstrate that splitting highly complex JSP instances into
balanced portions, for which partial schedules of good quality can be reliably
found within tight runtime limits, leads to significantly better global solutions
than obtainable with single-shot ASP modulo DL optimization in similar runtime.
Related works taking advantage of single- \citep{abjoossctowa21a}
and multi-shot solving \citep{francescutto2021solving} by
\clingodl to tackle real-world scheduling problems evaluate threshold values
on DL variables and perform optimization by means of common 
\lstinline{#minimize} statements of \clingo rather than minimizing the
value of a DL variable like \lstinline{makespan} in Listing~\ref{prg:encoding}.
Applying a similar approach can be advantageous in our future work as it may
potentially improve computational efficiency as well as solution quality further
and is even a necessity to switch from the makespan as optimization objective to tardiness
w.r.t.\ deadlines, which are crucial in many application areas.
While Machine-based decomposition turned out to be helpful
for finding better schedules, the strategies presented in Section~\ref{subsec:decomposition}
can be regarded as naive heuristics based on straightforward instance properties,
and incorporating machine-learning approaches \citep{elscge22a,tagesc21a}
for more adept partitioning is another promising direction for future work.
Moreover, we aim to generalize our methods further, e.g.,
by considering flexible machine allocations and varying processing times,
and scale them up to large real-world scheduling problems with an order of magnitude more
operations than in synthetic benchmarks.
%
% In this work, different decomposition strategies have been proposed for solving the Job-shop Scheduling Problem (JSP) using a multi-shot Answer Set Programming with Difference Logic constraints to handle the decomposition approach and the problem constraints. The proposed model split the problem into sub-problems using different decomposition strategies and then optimized each separately while minimizing the Makespan. The proposed model has been developed to improve the performance by applying the overlap between TWs to fix the decomposition mistakes. In addition, the compression of each window is to fulfill the gaps that occurred during the optimization process. We tested our model on a set of benchmark instances and the experiments have shown that i) considering the bottleneck machines during the decomposition process is effective, ii) The overlap between TWs improves the solution quality, and iii) the compression of TWs is super practical, as it aided the proposed model to obtain better solutions in less computational time. Our work can be extended by linking the optimization model with a simulator that considers more realistic factors such as machine breakdowns, new job arrivals and order cancellations.
